---
title: "Wilson Replication Analysis"
output:
  html_document:
    toc: true
---



# Deidentify
First, we'll deidentify the data (salt and hash) and work with that 
```{r eval = FALSE}

d <- read.csv("~/Wilson-2014-just-think-replication/data/identified/HITResultsFor3VADEH0UHCXATAPEJ7DOH8HDMOJPSJ.csv", stringsAsFactors=F)
salt <- read.csv("~/Wilson-2014-just-think-replication/data/identified/salt.csv", stringsAsFactors=F, header = FALSE)[1,1]
d$id <- paste(d$WorkerId, salt, sep="") #salt
d$id <- unlist(lapply( d$id, function(id){ digest(id, algo="sha256" ) } )) #hash
d <- select(d,-c(HitId:Status, Answer.1)) # delete MTurk Id and other extra info
d <- d[order(d$id),] # reorder to not be identifiable with originals
#	write the deidentified files to the shared folder
write.csv(d,"~/Wilson-2014-just-think-replication/data/data.csv", row.names=F)
```

# Libraries
```{r, warning=FALSE, message=FALSE}
library(reshape2)
library(Hmisc)
library(dplyr)
library(ggplot2)
```

# Data Formatting
First we set the data up for easy analysis. Basically, this gets all the questions that were answered by the participant, and puts them in long form.
```{r}
d <- read.csv("~/Wilson-2014-just-think-replication/data/data.csv", stringsAsFactors=F)

da <- data.frame(id=character(),
                 variable=character(), 
                 value=character()) 

for(n in 1:nrow(d)) {
  p <- d[n,] # get one participant
  pat <- '.*question":"(.*)","answer.*' # get question name
  p_ans <- p[grepl(pat, p)] # get only those answered
  names(p_ans) <- sub(pat, "\\1", p_ans)
  
  pat2 <- '.*answer":(.*)}'
  p_ans[1,] <- sub(pat2, "\\1", p_ans)
  p_ans[1,] <- gsub("\\n", ' & ', p_ans, fixed=T) # separate activities
  p_ans[1,] <- gsub("[[:punct:]]", '', p_ans)
  
  # merge with id
  p_ans$id <- d[n,"id"]
  
  p_m <- melt(p_ans, id.vars="id")
  
  da <- rbind(da,p_m)
}
# variable is somehow a factor now, so let's change back to character
da$variable <- as.character(da$variable)
# only grad the time period of the free period
da$variable[grep("time_free-period",da$variable)] <- "timeFreePeriod"
# and get rid of time for now, and we could add back in if we want to take a look
da <- da[! grepl("time_", da$variable),]
table(da$id) # how many answers per participant?
```

# Create Checks

## Window checks
```{r}
da[grepl("windowCheck_", da$variable) & !duplicated(da$value),]
wChecks <- da %>% filter(grepl("windowCheck_", variable)) %>% # get windowChecks
  group_by(id) %>%
  mutate(false = grepl("false",value)) %>%
  summarise(num = length(unique(value)),
            falses = sum(false))
  
#get ids that don't pass window check (moved window or not active) - should only be for think condition
fail_window <- wChecks %>% filter(num > 1 | falses != 0)
fail_window <- fail_window$id
# get rid of window checks to be more manageable data
da <- da %>% filter(!grepl("windowCheck_", variable))
```

## Cast to wide form and make numeric
Cast to long form for easier manipulation
```{r}
dm <- dcast(da,id ~ variable)
```

And make numeric rows numeric
```{r}
smart_cast_numeric <- function(DF){
  numeric_DF <- DF
  for(i in 1:ncol(DF)){
  	numeric_DF[,i] <- all.is.numeric(DF[,i], what = c( "vector"), extras=c('.','NA','',NA))
	}
	return(numeric_DF)
}
dm <- smart_cast_numeric(dm)
```

Update fail_window for only those in the thinking condition
```{r}
fail_window <- dm[dm$id %in% fail_window & dm$condition == "think","id"]
```

## 12 minute check
```{r}
timeChecks <- dm %>% filter(is.na(timeFreePeriod)) # went more than 71 checks

# get ids that don't pass time check
fail_time <- unique(timeChecks$id)
```


## Manipulation check
Did they respond that they did the activities asked?
```{r}
# find if their condition matches what they think their condition was
fail_manip <- dm[dm$condition != dm$manipCheck,"id"]
```

## Activities check
Did they do any of the activities they weren't supposed to?
```{r}
disallowed_active <- c("asleep","phonetalk","phonetext","imchat","email","talk","work")
disallowed_think <- c(disallowed_active,"openwindow","videogame","read","puzzle","tvmovie","music","write")
d_think <- lapply(dm[,disallowed_think],function(x){sum(x) >2})
fail_think <- dm[dm$condition == "think" & rowSums(dm[,disallowed_think]) >2,"id"]
fail_active <- dm[dm$condition == "active" & rowSums(dm[,disallowed_active]) >2,"id"]
fail_cond <- c(fail_think,fail_active)
```


# Limiting the data
## Original
Criteria:

1. Participants did not spend more than 12 minutes on the task, indicating they were at their computer

```{r}
table(dm$id %in% fail_time,dm$condition) #which failed by condition?
dm1 <- dm %>% filter(!id %in% fail_time) # save new analysis dataframe
```

## Strict
Criteria:

1. Participants did not spend more than 12 minutes on the task, indicating they were at their computer
2. Participants in the thinking condition did not resize their window
3. Participants knew what condition they were in
4. Participants spent less than minutes on something they were not supposed to (based on condition)

```{r}
fail_all <- unique(c(fail_time,fail_window,fail_manip,fail_cond))
table(dm$id %in% fail_all,dm$condition) #which failed by condition?
dm2 <- dm %>% filter(!id %in% fail_all) # save new analysis dataframe
```


# Original Analysis

### Enjoyment plot and t-test
```{r}
ggplot(dm1,aes(x=enjoy, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.5) +
  theme_classic() + 
  scale_x_continuous(breaks=c(1.25:9.25), labels=c(1:9))
t.test(enjoy ~ condition, dm1)
```

### Mind Wandering plot and t-test
```{r}
ggplot(dm1,aes(x=wander, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.5) +
  theme_classic() + 
  scale_x_continuous(breaks=c(1.25:9.25), labels=c(1:9))
t.test(wander ~ condition, dm1)
```
### Ability to Concentrate plot and t-test
```{r}
ggplot(dm1,aes(x=concentrate, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.5) +
  theme_classic() + 
  scale_x_continuous(breaks=c(1.25:9.25), labels=c(1:9))
t.test(concentrate ~ condition, dm1)
```

# Strict Analysis
We do not yet have enough participants to run this...

### Enjoyment plot and t-test
```{r, eval=FALSE}
ggplot(dm2,aes(x=enjoy, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.4) +
  theme_classic()
t.test(enjoy ~ condition, dm2)
```

### Mind Wandering plot and t-test
```{r, eval=FALSE}
ggplot(dm2,aes(x=wander, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.4) +
  theme_classic()
t.test(wander ~ condition, dm2)
```
### Ability to Concentrate plot and t-test
```{r, eval=FALSE}
ggplot(dm2,aes(x=concentrate, fill=condition)) +
  geom_histogram(position="dodge", binwidth=.4) +
  theme_classic()
t.test(concentrate ~ condition, dm2)
```



df <- data.frame(x = c(0,0,1,2,2,2))

ggplot(df,aes(x)) + 
geom_histogram(binwidth=.3, origin = -0.25) + 
scale_x_continuous(breaks=0:2)
